Optimizing Structural Properties Of Neural Networks With Genetic Algorithms

### 2015-08-01 paper/paper.tex
text + script

A measure that is timeshift independent and maximized for functions of identical shape is the 
maximum of the cross correlation 
\begin{align}
f_c(g, g^\prime) = \max_t \left<g, g^\prime(\cdot - t)\right> / \sqrt{\left< g, g\right> \left<g^\prime, g^\prime \right>}.
\end{align}
Algorithmically, the signals are split into chunks which are correlated separately. This saves computational power and 
prevents minute differences in frequency to accumulate into a huge phase shift, i.e. the phase only has to remain relatively
constant over the timescale of a single chunk.

>>>>

A measure that is timeshift independent and maximized for functions of identical shape is the 
maximum of the cross correlation 
\begin{align}
f_c(g, g^\prime) = \max_t \left<g, g^\prime(\cdot - t)\right> / \sqrt{\left< g, g\right> \left<g^\prime, g^\prime \right>}.
\end{align}
Algorithmically, the signals are split into overlapping chunks which are correlated separately. 
This saves computational power and prevents minute differences in frequency to accumulate into 
a huge phase shift, i.e. the phase only has to remain relatively
constant over the timescale of a single chunk (i.e. about 10 seconds of simulated time).

This measure becomes problematic for functions that are very close to zero for a longer time 
(order of chunk size), but since we are going to work with superpositions of sinusoidals of 
different frequencies, this drawback is unproblematic.
